Stan Practice

### 2021-02-16 Stan/Stan Base Models.Rmd
Stan Models (With and Without Ant Interaction)

```{r}
data <- cactus[ ,c("Plot","Year_t","Survival_t1","ant_t","ant_t1","volume_t","volume_t1","repro_state_t1")]
data <- na.omit(data)
data$ant <- as.integer(data$ant_t)
## add columns for each ant classification so they can be binary
data$crem <- 0 ##2
data$liom <- 0 ##3
data$other <- 0 ##1
data$vacant <- 0 ##4
for(i in 1:nrow(data)){
  if(data$ant[i] == 1){data$other[i] <- 1}
  if(data$ant[i] == 2){data$crem[i] <- 1}
  if(data$ant[i] == 3){data$liom[i] <- 1}
  if(data$ant[i] == 4){data$vacant[i] <- 1}
}

>>>>

```{r}
data <- cactus[ ,c("Plot","Year_t","Survival_t1","ant_t","ant_t1","volume_t","volume_t1","repro_state_t1")]
data <- na.omit(data)
data$ant <- as.integer(data$ant_t)
## add columns for each ant classification so they can be binary
data$crem <- 0 ##2
data$liom <- 0 ##3
data$other <- 0 ##1
data$vacant <- 0 ##4
for(i in 1:nrow(data)){
  if(data$ant[i] == 1){data$other[i] <- 1}
  if(data$ant[i] == 2){data$crem[i] <- 1}
  if(data$ant[i] == 3){data$liom[i] <- 1}
  if(data$ant[i] == 4){data$vacant[i] <- 1}
}
data$Year_t <- as.factor(data$Year_t)
data$year <- as.integer(data$Year_t)
data$Plot <- as.factor(data$Plot)
data$plot <- as.integer(data$Plot)
